\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex
fix pull request comments

On a similar note, the requirements and scope of the project changed greatly
from week to week, and sometimes even within one day. We spent a lot of time
exploring concepts and features that were completely unrelated to the final
product. We also did not receive official specifications, such as the design of
the GUI Atticus wanted for the app, until very late in the development process.

@@

While not a disaster, we had some initial trouble getting started with Unity.
Different versions of Unity do not play well with each other, and it often runs
into bugs on older hardware, such as the laptops we had to work with.
Furthermore, a stable version of the Unity editor is not available on
GNU/Linux~\autocite{best2019}, so one of our team members had to install MacOS
in order to use it. We were able to resolve these issues in the first weeks of
the project, but it consumed some of our valuable time in July.

>>>>

On a similar note, the requirements and scope of the project changed greatly
from week to week, and sometimes even within one day. We spent a significant
amount of time exploring concepts and features that were completely unrelated to
the final product. We also did not receive official specifications, such as the
design of the GUI Atticus wanted for the app, until very late in the development
process.

@@

While not a disaster, we had some initial trouble getting started with Unity.
Different versions of Unity do not play well with each other, and it often runs
into bugs on older hardware, such as the laptops we had to work with.
Furthermore, a stable version of the Unity editor is not available on
GNU/Linux~\autocite{best2019}, so one of our team members had to install macOS
in order to use it. We were able to resolve these issues in the first weeks of
the project, but it consumed some of our valuable time in July.
